---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# deploycaret

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/deploycaret)](https://CRAN.R-project.org/package=deploycaret)
[![R-CMD-check](https://github.com/topepo/deploycaret/workflows/R-CMD-check/badge.svg)](https://github.com/topepo/deploycaret/actions)
<!-- badges: end -->

**This pre-release is available for feedback and experimenting.**

The goal of deploycaret is to provide fluent tooling to version, share, and deploy a trained [caret](https://topepo.github.io/caret) model. Functions handle both recording and checking the model's input data prototype, and loading the packages needed for prediction.

## Installation

~~You can install the released version of deploycaret from [CRAN](https://CRAN.R-project.org) with:~~

``` r
install.packages("deploycaret") ## not yet
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("topepo/deploycaret")
```

## Example

You can use the [caret](https://topepo.github.io/caret) package to train a model, with a wide variety of preprocessing and model estimation options.

```{r}
library(caret)
data(Sacramento, package = "modeldata")
Sacramento <- as.data.frame(Sacramento)

predictors <- Sacramento[, c("type", "sqft", "beds", "baths")]

set.seed(1)
rf_fit <-
  train(
    x = predictors,
    y = Sacramento$price,
    method = "ranger",
    tuneLength = 3,
    trControl = trainControl(method = "cv")
  )
rf_fit
```

You can **version** and **share** your model by [pinning](https://pins.rstudio.com/dev/) it, to a local folder, RStudio Connect, Amazon S3, and more.

```{r}
library(deploycaret)
library(pins)

model_board <- board_temp()
m <- modelops(rf_fit, "sacramento_rf_caret", model_board)
modelops_pin_write(m)
```

You can **deploy** your pinned model via a [Plumber API](https://www.rplumber.io/), which can be [hosted in a variety of ways](https://www.rplumber.io/articles/hosting.html).

```{r, eval=FALSE}
library(plumber)

pr() %>%
    modelops_pr_predict(m) %>%
    pr_run(port = 8088)
```

Make predictions with your deployed model by creating an endpoint object:

```{r}
endpoint <- modelops_endpoint("http://127.0.0.1:8088/predict")
endpoint
```

A model API endpoint deployed with `modelops_pr_predict()` will return predictions with appropriate new data.

``` r
new_sac <- head(predictors)

predict(endpoint, new_sac)
#> # A tibble: 20 x 1
#>      .pred
#>      <dbl>
#>  1 165042.
#>  2 212461.
#>  3 119008.
#>  4 201752.
#>  5 223096.
#>  6 115696.
#>  7 191262.
#>  8 211706.
#>  9 259336.
#> 10 206826.
#> 11 234952.
#> 12 221993.
#> 13 204983.
#> 14 548052.
#> 15 151186.
#> 16 299365.
#> 17 213439.
#> 18 287993.
#> 19 272017.
#> 20 226629.
```

## Contributing

This project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

- For questions and discussions about tidymodels packages, modeling, and machine learning, please [post on RStudio Community](https://community.rstudio.com/new-topic?category_id=15&tags=tidymodels,question).

- If you think you have encountered a bug, please [submit an issue](https://github.com/topepo/deploycaret/issues).

- Either way, learn how to create and share a [reprex](https://reprex.tidyverse.org/articles/articles/learn-reprex.html) (a minimal, reproducible example), to clearly communicate about your code.

- Check out further details on [contributing guidelines for tidymodels packages](https://www.tidymodels.org/contribute/) and [how to get help](https://www.tidymodels.org/help/).
